Faithful Variable Screening for\\ High-Dimensional Convex Regression

### 2015-05-19 tex/scam/experiments.tex
a

We study both the independent case where $P = N(0, I_p)$ and the
correlated case where $P$ is a correlated Gaussian Copula modified
slightly to satisfy the boundary flatness condition. We measure the
probability of exact selection in the independent case and the
probability of screening in the correlated case. We also study both
cases where the regression function is parametric (quadratic) and
cases where the regression function is nonparametric (softmax of
linear forms). In all our experiments, we mark a variable as selected
if either the AC estimate $\| \hat{f}_j \|_\infty$ or the DC estimate
$\| \hat{g}_k \|_\infty$ is larger than $10^{-6}$. We set $\lambda =
0.5 \sqrt{\frac{\log^2 np}{n}}$ for all the simulations.

@@

\begin{figure*}
\includegraphics[width=.4\textwidth]{figs/copula_marginal}
\caption{Marginal density of the Gaussian Copula and Uniform Mixture}
\label{fig:copula_marginal}
\end{figure*}

>>>>

We study both the independent case where $P = N(0, I_p)$ and the
correlated case where $P$ is a correlated Gaussian copula modified
slightly to satisfy the boundary flatness condition. We measure the
probability of exact selection in the independent case and the
probability of screening in the correlated case. We also study both
cases where the regression function is parametric (quadratic) and
cases where the regression function is nonparametric (softmax of
linear forms). In all our experiments, we mark a variable as selected
if either the AC estimate $\| \hat{f}_j \|_\infty$ or the DC estimate
$\| \hat{g}_k \|_\infty$ is larger than $10^{-6}$. We set $\lambda =
0.5 \sqrt{\frac{\log^2 np}{n}}$ for all the simulations.

@@

\begin{figure*}
\includegraphics[width=.4\textwidth]{figs/copula_marginal}
\caption{Marginal density of the Gaussian copula and uniform mixture}
\label{fig:copula_marginal}
\end{figure*}
